Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-04-16 Response to reviewers.tex

Option {\em a)} was actually closer to our initial intention when
submitting this paper, so we opted for it.

\begin{verbatim}
= Specific comments =

According to page 12, line 7 "the user interacts with the devices
(...) through the MUSES graphical interface inside his or her own
context". This is surprising. I have pictured MUSES as a hyper-visor
module but, according to this sentence, MUSES is a GUI that contains
every application the user has access to. I think further
clarification are needed about how the user interacts with his
applications and what this GUI the authors are describing is
exactly. Contexts in this sentence "(situation, connection, status)"
do not match contexts in figure 2 "(social, economical, political)".
\end{verbatim}

This observation is very much appreciated since it is true that what was written could lead to a missunderstanding. The description has been changed, and the context properly defined and explained.

@@

\begin{verbatim}
Page 13. The first reason to use a client/server architecture is that
the event correlation and self-adaptation processes need a very
powerful machine (a server), but this statement seems not be based on
any real experiment run by the authors or any previous references. In
addition, I find the second reason to user a client/server
architecture quite surprising. Quoting: "there are two clearly
separated parts in the system, namely the users (clients) and the
enterprise (server)" I think this is a very weak justification. I can
identify many other actors in the system: data providers (cloud
system, databases...), other workers in the enterprise (for corporate
applications), the friends of the user (for private applications),
external application providers... Hence, if the "second reason" is of
any real value, MUSES would have a P2P architecture. From my point of
view, the reasons given by the authors are too week and, in any case,
there is not really any necessity to justify 
why MUSES has a client/server architecture.
\end{verbatim}

The reviewer is right. We have rewritten the paragraph justifying the
use of a server machine due to its computational power, needed for
applying Data Mining and Machine Learning techniques over Big
Datasets, and also to centralise the data gathering of the system. We
have removed the text explaining the consideration of two parts in the
system.

\begin{verbatim}
Page 13, line 45 says all data in MUSES will be encrypted. It is not
clear if the authors mean "the Decision Table and the even logger", or
"all data in the devices, including personal data, contact list,
emails..." If it is the latter, authors should explain how MUSES
enforces this policy. Does it control all applications in the mobile
phone? Does the mobile phone run only white-listed applications? 
\end{verbatim}

We strongly agree with this and a detailed description of the encryption methods, that the second prototype of MUSES will implement, has been included.

### 2015-04-16 MUSES_vs_BYOD_solutions.tex
Aclarado lo de la encriptación, closes #14

As a summary, this application includes two modules: a \textit{controller} and an \textit{actuator}. The first one monitors the environment (context) and the user's behaviour, translating their actions in a sequence of events. These events, along with the patterns defining the user's conduct, are processed by the system in real-time by means of a Risk and Trust Analysis Engine (RT2AE) and an Event Correlation module. Then, a decision is taken in the corporate security operations centre (SOC) side, considering the RT2AE output and the set of security rules adapted to that specific user and context. The corresponding feedback is communicated to the user through the \textit{actuator}, which is also in charge of triggering the recommended actions to stop the user's or application's doings, in case it is required.

The designed MUSES architecture is shown in Figure \ref{fig:architecture}. It is a \textit{client/server} approach in which the \textit{client} program can be installed in every user's mobile or portable device, independently of the platform (operating system and type of device). The \textit{server} side can be installed in the corporate SOC. Both sides are connected through a secure channel (using HTTPS) over the Internet. In that figure just the high-level components in each part are shown, along with the information flows labelled as `Info XX'. %FERGU: esto no se si es de muses y posiblemente esté por terminar, pero quitad las comillas raras

@@

The system considers two working modes for every device: online and offline. In the \textit{online} mode the device can connect with the MUSES server, so it can request the server to make a decision. On the other hand, in \textit{offline} mode the server cannot be reached by the device (there is not an available connection between them), so all the decisions should be made locally.
This is done using an up-to-date copy on the Decision Table inside the Local database, which contains decisions for any type of detected event, along with the default actions to be performed if no rule is met. Anyway, in this mode, the gathered information by the sensors in the device  is stored for later submission to the server side (when a connection is available), in order to be processed in the knowledge refinement process.
Moreover, when switching from offline to online mode, the device  receives an updated copy of the Decision Rules (the so-called Device Policies), as a kind of antivirus database, in order to work again perfectly in offline mode (if the connection is lost).

All data in MUSES  is encrypted. %FERGU: esta frase esta un poco forever alone aquí, falta algo por mencionar? Que tecnología se usará, cómo se encriptará y todo eso.
% Antonio - Sí, se va a comentar mejor en uno de los Issues. ;)

>>>>

As a summary, this application includes two modules: a \textit{controller} and an \textit{actuator}. The first one monitors the environment (context) and the user's behaviour, translating their actions in a sequence of events. These events, along with the patterns defining the user's conduct, are processed by the system in real-time by means of a Risk and Trust Analysis Engine (RT2AE) and an Event Correlation module. Then, a decision is taken in the corporate Security Operations Centre (SOC) side, considering the RT2AE output and the set of security rules adapted to that specific user and context. The corresponding feedback is communicated to the user through the \textit{actuator}, who decides to comply or not with the policy. As was mentioned before, MUSES depends on the MUSES Aware applications to be able to really stop the application if the risk is dangerously high. In case that MUSES cannot kill the application process, and if the user decides to continue performing a risky action, the user trust value will decrease.

The designed MUSES architecture is shown in Figure \ref{fig:architecture}. It is a \textit{client/server} approach in which the \textit{client} application can be installed in every user's mobile or portable device, independently of the platform (operating system and type of device). The \textit{server} side can be installed in the corporate server. Both sides are connected through a secure channel (using HTTPS) over the Internet. In that figure just the high-level components in each part are shown, along with the way the information flows in the system. %FERGU: esto no se si es de muses y posiblemente esté por terminar, pero quitad las comillas raras

@@

The system considers two working modes for every device: online and offline. In the \textit{online} mode the device can connect with the MUSES server, so that it can request the server to make a decision. On the other hand, in \textit{offline} mode the server cannot be reached by the device because there is not an available connection between them, so all the decisions are made locally.
This is done using an up-to-date copy on the Decision Table inside the Local database, which contains decisions for any type of detected event, along with the default actions to be performed if no rule is met. Anyway, in this mode, the gathered information by the sensors in the device  is stored for later submission to the server side (when a connection is available), in order to be processed in the knowledge refinement process.
Moreover, when switching from offline to online mode, the device  receives an updated copy of the Decision Rules (the so-called Device Policies), as a kind of antivirus database, in order to work again perfectly in offline mode (if the connection is lost).

All flows of information in MUSES are encrypted with AES with 128-bit key in GCM mode \cite{viega2005use}, following the recommendations fo the Fact Sheet on Suite B Cryptography \cite{salter2012suite}. Also, the MUSES server authenticates to the MUSES client by means of a self-signed certificate. The authentication of the users is based on Spring Security, which is a Java/Java EE framework that provides authentication, authorization and other security features for enterprise applications. And finally, MUSES makes use of the fact that current operating systems for mobile devices provide encrypted data containers by default, like the feature used in Android Work. %FERGU: esta frase esta un poco forever alone aquí, falta algo por mencionar? Que tecnología se usará, cómo se encriptará y todo eso.
% Antonio - Sí, se va a comentar mejor en uno de los Issues. ;)
